mir\_eval

### 2014-05-01 paper/paper.tex
Abstract

\begin{document}
%
\maketitle
%
\begin{abstract}

\end{abstract}
%
\section{Evaluating MIR Algorithms}\label{sec:introduction}

>>>>

\begin{document}
%
\maketitle
%
\begin{abstract}
Central to the field of MIR research is the evaluation of algorithms used to extract information from music data.  We present mir\_eval, an open source software library which provides a transparent and easy-to-use implementation of the most common metrics used to measure the performance of MIR algorithms.  In the present work, we enumerate the metrics implemented by mir\_eval and quantitatively compare each to an existing implementation.  When the score reported by mir\_eval differs substantially from the reference, we detail the differences in implementation.  We also provide a brief overview of mir\_eval's architecture, design, and intended use.
\end{abstract}
%
\section{Evaluating MIR Algorithms}
